---
title: "Team Report"
author: "Felix Baez-Santiago, Chris Anderson, Austin Nebel"
date: "2/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#importing dataset from web scrap
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv")
str(choco)
```
# Question 1.1 
How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.
```{r}
hist(choco$Rating, main='Distribution of Ratings', xlab='Rating')
boxplot(choco$Rating, main='Distribution of Ratings')
```
The rating distribution is bimodal, left skewed, most of the data is in between 2.5 and 4.0 with an extreme gap in the the middle and there are at least 4 outliers present. 

# Question 1.2
How does the number of ratings depend on the location of the company? Draw a bar chart of the number of reports.
```{r}
barplot(table(choco$Location), main='Number of Ratings by Location', xlab='Year', ylab='Count', las  = 2)
# text(x = table(choco$location), labels = names(choco$location), srt = 45, xpd = Na)
```
# Question 1.3
Do ratings depend on the cocoa percentage of a chocolate bar? Create both numerical and graphical summaries, and explain. [Hint: Think about why the scatterplot is not a very good choice for visualization here.]
```{r}
cor(choco$Rating, choco$Cocoa_Percent)
plot(choco$Rating, choco$Cocoa_Percent, main='Scatter Plot of Cocoa Percentage and Rating', xlab='Rating', ylab='Cocoa Percent')
```

# Question 1.4
How do different bean origins compare in terms of the flavor of chocolates? Are beans from some places better than the other? Create both numerical and graphical summaries, and explain.
```{r}
or <- choco[,c("Bean_Origin", "Rating")]
table(or)

origin_counts <- table(choco$Rating, choco$Bean_Origin)
barplot(origin_counts, las=2, cex.names=0.45)

origin_by_rating <-  or$Rating ~ or$Bean_Origin
boxplot(origin_by_rating, las=2, cex.axis=0.45)
```


# Question 1.5
Brainstorm two analyses you would like to perform (with your teammates). Describe in plain language what comparisons are you making. Create suitable numerical and graphical summaries for your analyses. Describe the results.

### # Analysis 1: How are cocoa beans rated based on origin?
```{r}
rows <- choco[choco$Bean_Origin == "U.S.A.", ]
barplot(table(rows[, "Bean_Origin"], rows[, "Rating"] ), main = "Cocoa Beans from the U.S.")
print(summary(rows[, "Rating"]))

rows2 <- choco[choco$Bean_Origin == "Colombia", ]
barplot(table(rows2[, "Bean_Origin"], rows2[, "Rating"] ), main = "Cocoa Beans from Colombia")
print(summary(rows2[, "Rating"]))

rows3 <- choco[choco$Bean_Origin == "Ghana", ]
barplot(table(rows3[, "Bean_Origin"], rows3[, "Rating"] ), main = "Cocoa Beans from Ghana")
print(summary(rows3[, "Rating"]))
```
We compared different bean origins based on rating. Out of these 3 countries we found that Colombia exports the most cocoa beans. The US seems to produce high quality chocolates as it has many rated in a range of 3 and 3.75. There seems to be an association between producing more chocolates and having a higher rating.

### Analysis 2: What years had the highest-rated chocolate?
First, lets check the amount of ratings per year.
```{r}
yr <- choco[,c("Date", "Rating")]

year_counts <- table(choco$Rating, choco$Date)
table(yr)
barplot(year_counts, cex.names=0.65, beside=TRUE)
```

Next, lets look at 2 box plots; the first is shows how each rating is dispersed across all years, and the second shows all of the ratings for each year.
```{r}
origin_by_rating <-  yr$Date ~ yr$Rating
boxplot(origin_by_rating, cex.axis=0.65)

origin_by_rating <-  yr$Rating ~ yr$Date
boxplot(origin_by_rating, cex.axis=0.65)
```

From the first box plot it can be seen that the rating of 3 was the used throughout a large portion of the years that chocolates were rated. The second box plot tells us that for each year the ratings almost always had an average that was either 3.0 or 3.25, telling us that most years were very similar in their chocolate ratings. However, in the second box plot the 4 highest ratings (3.25-4) had the majority of their ratings between the years of 2012 and 2016, which suggest that those were the years that scored the highest in chocolate.
